---
title: "List Columns"
author: "Lectured by Jeff Goldsmith"
date: "2022-11-01"
output: github_document
---

```{r library, include = FALSE}
library(tidyverse)
library(rvest)
```

## *Lists*

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

Let's look at a list.
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_char    = c("My", "name", "is", "Jeff"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items
```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


## *`for` loops*

```{r basic structure, eval = FALSE}
input = list(...)
output = list(...)
 for (i in 1:n) {
   output[[i]] = f(input[[i]])
 }
```

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r write function}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
# I think we can do a loop for this...
```

```{r}
output = vector("list", length = 4)

for(i in 1:4) {
 output[[i]] = mean_and_sd(list_norms[[i]]) 
}

output
```


### *`map`*

Goal of *map* is to clarify the *loop* process.

```{r map basic structure, eval = FALSE}
output = map(input, f)
```

```{r easier way to do loops}
map(list_norms, mean_and_sd)
```

what about other functions?
```{r}
map(list_norms, summary)
```

map variants...
```{r}
map_dbl(list_norms, median)

df = map_df(list_norms, mean_and_sd)
```

## List columns

```{r}
listcol_df = tibble(
  name = c("a", "b", "c", "d"),
  norm = list_norms
)

listcol_df[["norm"]]

output = map(listcol_df[["norm"]], mean_and_sd)
```

can we add list columns, and then what

```{r}
listcol_df %>% 
  mutate(
    m_sd = map_df(norm, mean_and_sd)) %>% 
  select(-norm)
```

What about something more realistic?
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's nest within weather stations.
```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
```

Really is a list column!
```{r}
weather_nest_df[["data"]]
```


### Linear regression

```{r}
# I just want to do linear regression using the tmin & tmax variables nested inside the "data" list column, 
# and only the first list.
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[3]])
```

Let's write a short lil of function.
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest_df[["data"]][[1]])

map(weather_nest_df[["data"]], weather_lm)
```

Can I do all these in a tidy way?
```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm) 
    # don't need to specify the dataset because I'm piping from that dataset. Just indicate the column name "data".
  )
```

#### unnesting

```{r}
weather_nest_df %>% 
  unnest(data) 
```


## Napolean review

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

```{r}
dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) 

dynamite_reviews %>% 
  select(-urls) %>% 
  unnest(reviews)
```


