---
title: "List Columns"
author: "Lectured by Jeff Goldsmith"
date: "2022-11-01"
output: github_document
---

```{r library, include = FALSE}
library(tidyverse)
library(rvest)
```

## *Lists*

In R, vectors are limited to a single data class - all elements are characters, or all numeric, or all logical.
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

**Lists provide a way to store anything we want.**

Let's create a list.
```{r}
# l is a list of different variables...
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_char    = c("My", "name", "is", "Jeff"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE),
  summary     = summary(rnorm(1000))
)

l
```

Different ways to access list items:
```{r}
# 1) Use the dollar sign $  - Show me all the values for the variable "vec_numeric" in the list "l".
l$vec_numeric

# 2) Show me the 3rd variable in the list "l".
l[[3]]

# 3) Show me the values for the variable "mat" in the list "l".
l[["mat"]]
```


## *`for` loops*

This is the basic structure of `for` *loops*:
```{r basic structure, eval = FALSE}
input = list(...)
output = list(...)
 for (i in 1:n) {
   output[[i]] = f(input[[i]])
 }
```

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms) # Is list_norms a list?
```

Now I want to take the mean and sd of the four items (a, b, c, d) in the list above.
```{r write function}
mean_and_sd = function(x) {
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x)
}
```

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[["c"]])
mean_and_sd(list_norms[[4]])
# I think we can do a loop for this...
```

Instead of copy and paste the same argument over and over again, and change the number of list_norms every time, we can do a `for` *loop*.
```{r}
mean_sd = vector("list", length = 4) # The vector type is a list and it has 4 lists.

for(i in 1:4) {
 mean_sd[[i]] = mean_and_sd(list_norms[[i]]) 
}

mean_sd
```


### *`map`*

Goal of *map* is to clarify the *loop* process. If I use `map` I don't need to define the output.

This is a basic structure of a `map` function:
```{r map basic structure, eval = FALSE}
output = map(input, f) # f means function
```

In the examples below, I can use one line of code to get exactly the same thing as I did with the `for` *loop* above.
```{r easier way to do loops}
map(list_norms, mean_and_sd)
```

What if I want to use other functions?
```{r}
map(list_norms, summary)
# I can get a summary of mathematical computation.
```

**map variants**...
```{r}
map_dbl(list_norms, median) # show all the results in one line instead of showing them one by one separately.

df = map_df(list_norms, mean_and_sd) #show the results like a dataframe

df

# `map2` is helpful when our function has two arguments.
# Eg.  map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```

## List columns

Now that I create a new dataframe called *listcol_df*, and it consists of two variables.
One variable called `name` with four "values" *a*, *b*, *c*, *d*.
Another variable called `samp` that is a list (In this case, I am using the list which we created above - `list_norms`).

Then I map the `mean_and_sd` function over the list, but how do I save the results into the same dataframe `listcol_df`?
```{r}
listcol_df = 
  tibble(
  name = c("a", "b", "c", "d"),
  samp = list_norms)

listcol_df[["samp"]]

map_df(listcol_df[["samp"]], mean_and_sd)
```

Use `mutate`!
```{r}
listcol_df = 
  listcol_df %>% 
  mutate(
    m_sd = map_df(samp, mean_and_sd)) %>% 
  select(-samp)
```

What about something more realistic?

## Nested data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's nest within weather stations.
```{r}
weather_nest = 
  weather_df %>% 
  nest(data = date:tmin) # Collapsed everything from date to tmin and put them into a new variable "data".
```

Really is a list column!
```{r}
weather_nest[["data"]]

# Or we can also do this:
weather_nest %>% pull(data)
```

### Unnesting

We can also unnest data!
```{r}
weather_nest %>% 
  unnest(data) 
```

## Linear regression

Suppose we want to fit a simple linear regression for `tmax` and `tmin` for each station-specific dataframe.

```{r}
# I just want to do linear regression using the tmin & tmax variables nested inside the "data" list column, 
# and only the first list.
weather_nest[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[3]])
#very tedious, let's write a function...
```

Let's write a function.
```{r}
# I'll name my function "weather_lm" and when I put in a dataframe (df), run the following function..
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

# Now test my function:
weather_lm(weather_nest[["data"]][[1]])

# Instead of repeating the function many times for different set of list, use map:
map(weather_nest[["data"]], weather_lm)
```

How do we store the output of the linear regressions in the same dataframe? **Mutate**!
```{r}
weather_nest = 
  weather_nest %>% 
  mutate(
    model = map(data, weather_lm)) 
    # don't need to specify which dataset because I'm piping from that dataset. Just indicate the column name "data".

weather_nest
```


## Revisiting Napoleon review

1) Create a function first.
```{r}
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text)
}
```

2) Then, create a variable that read the url.
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

3) Map the function to the all the url pages. These two options won't show which page each review comes from.
```{r}
# Option 1
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews_1 = bind_rows(output)

# Option 2
dynamite_reviews_2 = map_df(vec_urls, read_page_reviews)
```

4) Option 3: Use dataframe and list columns.
```{r}
dynamite_reviews_3 = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) 

dynamite_reviews_3 %>% 
  select(-urls) %>% 
  unnest(reviews)
```


