---
title: "Simulation"
author: "Lectured by Jeff Goldsmith"
date: "2022-11-03"
output: github_document
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(tidyverse)
```

### Quick shorthand

* `shift` + `option` and then select the big chunk that you want to delete. 

repeat efgf
repeat efgf
repeat efgf
repeat efgf
repeat efgf

* `ctrl` + `F` find the word that you want to change. Replace with the other words.


## Simulation: Mean and SD for one ***n*** 

Generating a sample mean from a normal distribution...

As usual, create a function first.
```{r create a function first}
sim_mean_sd = function(n_obs, mu = 7, sigma = 4) {
  
    x = rnorm(n = n_obs, mean = mu, sd = sigma)
  
  tibble(
      mu_hat = mean(x),
      sigma_hat = sd(x))
}
```

Then, test if the function works properly.
```{r}
sim_mean_sd(n_obs = 30)
```

If we run the above code 100 times, we will get 100 different values every time. But we can use `for` *loop* or `map`!
```{r use for loop}
output = vector("list", length = 100)
for (i in 1:100) {
  output[[i]] = sim_mean_sd(n_obs = 30)
}

# make the results look like a tibble:
bind_rows(output)
```

We can also use list columns.
```{r}
sim_results = 
  # I want to create a dataframe that has expanded rows that do the following:
  expand_grid(   # expand_grid is like tibble...
    sample_size = 30,  # I want a column for sample_size
    iteration = 1:100) %>%   # Another column for iteration, and the rows go from 1 to 100
  # Then create a new column that calculate mean and sd using the function we created.
  mutate(
    estimate_measures = map(sample_size, sim_mean_sd)) %>% 
  unnest(estimate_measures)
```

We can make a plot to look at the distribution of all the mean and sd.
```{r}
sim_results %>% 
  ggplot(aes(x = mu_hat)) + 
  geom_density()

# Uhmmmm... It kinda look like a "normal" distribution.
```

#### What about changing the sample size?

I need to input a list 
```{r}
sim_results_2 = 
  expand_grid(   
    sample_size = c(30, 60, 120, 240), 
    iteration = 1:100) %>%   
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)) %>% 
  unnest(estimate_df)
```

```{r}
sim_results_2 %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) + 
  geom_violin()
```
```{r, eval = FALSE}
sim_results_2 %>% 
  mutate(
    sample_size = str_c("N = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  group_by(sample_size) %>% 
  summarize(emp_st_err = sd(mu_hat)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat)) + 
  geom_violin()
```

```{r}
sim_results_3 = 
  expand_grid(   
    sample_size = c(30, 60, 120, 240), 
    true_sigma = c(3, 6),
    iteration = 1:100) %>%   
  mutate(
    estimate_df = 
      map2(.x = sample_size, .y = true_sigma, ~sim_mean_sd(n_obs = .x, sigma = .y))) %>%  # ~ tells R that .x and .y go into this function.
  unnest(estimate_df)
```

```{r}
sim_results_3 %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() + 
  facet_grid(. ~ true_sigma)
```

The `cache = TRUE` argument in a code chunk can be helpful:
When it run the code one time, it will save the results. So when we knit the document, it will not take super long time to rerun the code again.
But we must pay attention to that, especially when we change the code, it will not recognize the changes. 
