---
title: "Writing Functions"
author: "Lectured by Jeff Goldsmith"
date: "2022-10-27"
output: github_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(rvest)

set.seed(1) 
```

# Write Functions

If we use the same code more than twice, write a function.

### Let's get some Z-scores!

Let's compute the z-score version of a list of numbers.
```{r x vec}
x_vec = rnorm(25, mean = 7, sd = 4)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Suppose we want to do this often.
```{r function x vec}
# z_scores = function(ARGUMENTS) {
  
#  BODY OF FUNCTION
#  }

z_scores = function(x){
  z = (x - mean(x)) / sd(x)
  
  z
}
```

```{r}
z_scores(x = x_vec)

z_scores(x = 1:10)

z_scores(x = rbinom(1000, 1, 0.6))

z_scores(x = 3) # can't do this because if x is only one number, R can't compute the sd of just one number.

z_scores(x = "My name is Jeff")
```

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")}
  else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")}
  
  z = mean(x) / sd(x)
  
  z
}
```

```{r}
z_scores(x = 3)

z_scores(x = "My name is Jeff")
```

## Let's have multiple outputs

```{r}
mean_and_sd = function(x) {
  mean_x = mean(x)
  sd_x = sd(x)
  
#How do I return both of these? Create a tibble!
  tibble(
    mean = mean(x),
    sd = sd_x)
}

mean_and_sd(x = x_vec)
```


## Let's start with simulations

```{r}
x_vec = rnorm(n = 25, mean = 7, sd = 4)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)

# If we run this code chunk many times, we will get different values every time.
```

But what if we want to change the n, mean, and sd and run the over and over again? Simulation!

```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  x = rnorm(n = n_obs, mean = true_mean, sd = true_sd)
  tibble(
    mean = mean(x),
    sd = sd(x)
  )
}
```

How does the function work?
```{r}
sim_mean_sd(n_obs = 25, true_mean = 10, true_sd = 5)

# we can also not name out the argument, just put the numbers in.
sim_mean_sd(2500, 10, 7)
```


## Fixing bad stuff

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```
What if I want to get 10 pages of the review? I would have to copy and paste the code chunk above 10 times!

We can do the following instead! Save our lives!

Write a function to get reviews.
```{r}
read_page_reviews = function(url) {
  dynamite_html = read_html(url)

  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Let's try with a url:
```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(base_url, c(1:5))

dynamite_reviews = 
  bind_rows(
    read_page_reviews(vec_url[1]),
    read_page_reviews(vec_urls[2]),
    read_page_reviews(vec_urls[3]),
    read_page_reviews(vec_urls[4]),
    read_page_reviews(vec_urls[5])
  )

dynamite_reviews

# Page 3 doesn't work with this code because there is a picture in one of the comment.
```

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```


## Variables Scoping and Names

Variables that we created inside a function stay inside the function. If we try to search for the variables outside the function, they don't exist. 

But we also don't want to create a variable outside a function and use that variable inside a function because then R will step out of the function to look for that variable. This can potentially cause us problem.

